A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-22 fivebranes/fact.tex
e36

We consider this decomposition at the level of the local $L_\infty$ algebra $\cG_Z$.
Recall that the Chevalley--Eilenberg cochains of this local $L_\infty$ algebra is the restricted factorization algebra~$\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\cG_Z)$. 
For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\cG_Z(U)^{(n)}\subset \cG_Z(U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action.
As a corollary of the proposition, we get a product decomposition 
\beqn
\label{eqn:Gdecomp}
\cG_Z = \bigoplus_{n \geq -1} \cG^{(n)} .
\eeqn
In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.

%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
%Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
%\[
%\cG_Z (U)  \bigoplus_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
%\]
%is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
%In this way, the assignment 
%\[
%\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
%\]
%defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.

@@

The weight zero summand $\cG_Z^{(0)}$ is special because it carries the induced structure of a local $L_\infty$ algebra on $Z$ inherited from the $L_\infty$ algebra $\cL_{sugra}$.
As a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
We will prove the following.

@@

%Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

@@

%\begin{prop}
%Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
%There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
%\begin{itemize}
%\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
%\[
%\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
%\]
%which is dense at the level of cohomology. 
%\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
%\beqn\label{eqn:decomp3}
%\Bar{\pi}_{*} \cL_{sugra} = \bigoplus_{n \geq -1} \cV_{n} 
%\eeqn
%\item[(3)]
%In weight zero, there is an equivalence of local Lie algebras on $Z$ 
%\[
%\cV_0 \simeq \cE(3|6)|Z 
%\]
%where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
%\end{itemize}
%\end{prop}

@@

In \cite{KR2} the following weight decomposition of $E(5|10)$ is constructed.
Denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in the five-fold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
Assign the following weights to the super Lie algebra $E(5|10)$. 
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[\d w_1 \d z_1] \in \Omega^{2,cl}(\Hat{D}^5)$ carries weight $+1 - 1 = 0$. 
(If we think about the odd part as the space of closed two-forms then equivalently this grading translates to the one-form symbol $\d(-)$ as carrying weight $-1/2$.)
\end{itemize} 
The weight grading is concentrated in degrees $\geq -1$. 
In particular, there is a decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \til V_{-1} \times \bigoplus_{n \geq 0} V_n 
\eeqn
with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$.

At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\beqn\label{eqn:decomp2}
\Hat{E(5|10)} = \bigoplus_{n \geq -1} V_n
\eeqn
We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
Here $V_{-1}$ is a $\C$-extension of $\til V_{-1}$ defined in the decomposition \eqref{eqn:decomp1}.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.

@@

We have seen that $\cG$ is given as the sheaf of sections of a pro vector bundle. 
In fact, the local $L_\infty$ algebra $\cG$ came with a natural decomposition 
\[
\cG = \bigoplus_{k \geq -1} \cG^{(k)} .
\]
There is a related local $L_\infty$ algebra 
\beqn
\til \cG \define \bigoplus_{k \geq 0} \cG^{(k)}
\eeqn
where we simply forget the weight $-1$ component. 
These product decompositions also hold at the level of compactly supported sections.

This weight grading on $\cG$ induces a filtration on the factorization algebra \eqref{eqn:factgrad} and on its $!$-dual 
\beqn
\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bu(\cG_{c}).
\eeqn
We will focus just on the $!$-dual factorization algebra.
To construct the filtration, first consider the natural filtration on the local Lie algebra $\cG$ induced by the grading
\beqn
\cG = F^0 \cG \supset F^1 \cG \supset \cdots 
\eeqn
where for $N \geq 1$ we have
\beqn
F^N \cG = \cG^{(\geq N-2)} = \bigoplus_{j \geq N-2} \cG^{(j)} ,
\eeqn
and similarly for $\til \cG$. 
If we define 
\beqn
\cG_1 \define \cG / \cG^{(\geq 0)} 
\eeqn
and for $N > 1$
\beqn\label{eqn:gN}
\cG_N \define \cG / \cG^{(\geq N-1)} , \quad \til \cG_N \define \til \cG / \cG^{(\geq N-1)} ,
\eeqn
then the associated graded local Lie algebras $\op{Gr} \cG$ and $\op{Gr} \til{\cG}$ satisfy $\op{Gr} \cG = \op{colim} \cG_N$ and $\op{Gr} \til \cG = \op{colim} \til \cG_N$.
These filtrations also hold at the level of compactly supported sections.

>>>>

We consider this decomposition at the level of the local $L_\infty$ algebra $\cG_Z$.
Recall that the Chevalley--Eilenberg cochains of this local $L_\infty$ algebra is the restricted factorization algebra~$\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\cG_Z)$. 
For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\cG_Z(U)^{(n)}\subset \cG_Z(U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action.
As a corollary of the proposition, we get a product decomposition 
\beqn
\label{eqn:Gdecomp}
\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
\eeqn
In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.

%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
%Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
%\[
%\cG_Z (U)  \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
%\]
%is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
%In this way, the assignment 
%\[
%\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
%\]
%defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $Z$.

@@

The weight zero summand $\cG_Z^{(0)}$ is special because it carries the induced structure of a local $L_\infty$ algebra on $Z$ inherited from the $L_\infty$ algebra $\cL_{sugra}$.
As a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
We will prove that it is equivalent to a local Lie algebra version of the exceptional super Lie algebra $E(3|6)$.

By local version, we mean a version of $E(3|6)$ which exists as a sheaf of super Lie algebras of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$ on any complex threefold $Z$ equipped with a square-root of its canonical bundle.
The even part of this sheaf is simply a semi-direct product 
\beqn
\Vect^{hol}(Z) \oplus \sl(2) \otimes \cO_Z .
\eeqn
Notice the similarity with the even part of $E(3|6)$ in equation \eqref{eqn:evenE36}. 
The odd part is 
\beqn
\Omega^{1,hol}(Z, K^{-1/2}_Z) \otimes \C^2 
\eeqn
Again, we observe the similarities with the odd part of $E(3|6)$ given in equation \eqref{eqn:oddE36}. 
The Lie bracket on this sheaf of super vector spaces is defined analogously to the bracket on $E(3|6)$. 
In particular, the bracket operations only involve holomorphic differential operators and hence extends to a local dg super Lie algebra structure on the Dolbeault resolution of the above holomorphic vector bundles. 
We denote this local dg super Lie algebra by $\cE(3|6)$.

When $Z = \C^3$ the $\infty$-jets at $0 \in \C^3$ of the local Lie algebra $\cE(3|6)$ is equivalent to the exceptional super Lie algebra $E(3|6)$.

@@

%Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

@@

%\begin{prop}
%Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
%There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
%\begin{itemize}
%\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
%\[
%\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
%\]
%which is dense at the level of cohomology. 
%\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
%\beqn\label{eqn:decomp3}
%\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
%\eeqn
%\item[(3)]
%In weight zero, there is an equivalence of local Lie algebras on $Z$ 
%\[
%\cV_0 \simeq \cE(3|6)|Z 
%\]
%where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
%\end{itemize}
%\end{prop}

@@

In \cite{KR2} the following weight decomposition of $E(5|10)$ is constructed.
Denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in the five-fold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
Assign the following weights to the super Lie algebra $E(5|10)$. 
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[\d w_1 \d z_1] \in \Omega^{2,cl}(\Hat{D}^5)$ carries weight $+1 - 1 = 0$. 
(If we think about the odd part as the space of closed two-forms then equivalently this grading translates to the one-form symbol $\d(-)$ as carrying weight $-1/2$.)
\end{itemize} 
The weight grading is concentrated in degrees $\geq -1$. 
In particular, there is a decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
\eeqn
with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$.

At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\beqn\label{eqn:decomp2}
\Hat{E(5|10)} = \prod_{n \geq -1} V_n
\eeqn
We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
Here $V_{-1}$ is a $\C$-extension of $\til V_{-1}$ defined in the decomposition \eqref{eqn:decomp1}.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.

@@

We have seen that $\cG$ is given as the sheaf of sections of a pro vector bundle. 
In fact, the local $L_\infty$ algebra $\cG$ came with a natural decomposition 
\[
\cG = \prod_{k \geq -1} \cG^{(k)} .
\]
There is a related local $L_\infty$ algebra 
\beqn
\til \cG \define \prod_{k \geq 0} \cG^{(k)}
\eeqn
where we simply forget the weight $-1$ component. 
These product decompositions also hold at the level of compactly supported sections.

This weight grading on $\cG$ induces a filtration on the factorization algebra \eqref{eqn:factgrad} and on its $!$-dual 
\beqn
\left(\Bar{\pi}_*\Obs_{sugra}\right)^! = \clie_\bu(\cG_{c}).
\eeqn
We will focus just on the $!$-dual factorization algebra.
To construct the filtration, first consider the natural filtration on the local Lie algebra $\cG$ induced by the grading
\beqn
\cG = F^0 \cG \supset F^1 \cG \supset \cdots 
\eeqn
where for $N \geq 1$ we have
\beqn
F^N \cG = \cG^{(\geq N-2)} = \prod_{j \geq N-2} \cG^{(j)} ,
\eeqn
and similarly for $\til \cG$. 
If we define 
\beqn
\cG_1 \define \cG / \cG^{(\geq 0)} 
\eeqn
and for $N > 1$
\beqn\label{eqn:gN}
\cG_N \define \cG / \cG^{(\geq N-1)} , \quad \til \cG_N \define \til \cG / \cG^{(\geq N-1)} ,
\eeqn
then the associated graded local Lie algebras $\op{Gr} \cG$ and $\op{Gr} \til{\cG}$ satisfy $\op{Gr} \cG = \op{colim} \cG_N$ and $\op{Gr} \til \cG = \op{colim} \til \cG_N$.
These filtrations also hold at the level of compactly supported sections.
